Advi recognizes the keystrokes listed below when drawing on the slide.

\subsection*{Survival command kit when scratch drawing}

\noindent
\begin{tabularx}{\linewidth}{clcX}
\ikey{\char94G}{quit}{End of scratch drawing.}
\ikey{Esc}{settings}{Enter the scratch drawing settings mode.}
\end{tabularx}

In the scratch drawing settings mode, the cursor is modified and you
can set some charateristics of the scratch drawing facility.
When in doubt, press

\begin{itemize}
 \item press \key{?} to get help,
% \item press \key{\char94G} to quit scratching immediately,
 \item press \key{Esc} to quit the setting mode.
\end{itemize}

\vspace{\stretch{1}}

\newpage

\subsection*{Scratch drawing settings mode keys}

When in the scratch drawing settings mode, the following keys have the
following respective meanings:

\subsubsection*{Setting the drawing line color}

\noindent
\begin{tabularx}{\linewidth}{clcX}
\ikey{$?$}{help}{Give the list of settings available.}
\ikey{b}{blue}{Set the color of the font to blue.}
\ikey{c}{cyan}{Set the color of the font to cyan.}
\ikey{g}{green}{Set the color of the font to green.}
\ikey{k}{black}{Set the color of the font to black.}
\ikey{m}{magenta}{Set the color of the font to magenta.}
\ikey{r}{red}{Set the color of the font to red.}
\ikey{w}{white}{Set the color of the font to white.}
\ikey{y}{yellow}{Set the color of the font to yellow.}
\ikey{B}{more blue}{Increment the blue component of the color.}
\ikey{G}{more green}{Increment the green component of the current color.}
\ikey{R}{more red}{Increment the red component of the current color.}
\ikey{$+$}{positive increment}{Set the color increment to positive.}
\ikey{$-$}{negative increment}{Set the color increment to negative.}
\ikey{$q$}{quit}{Quit scratching mode.}
\ikey{Escape}{quit}{Quit scratching mode.}
\end{tabularx}

\subsubsection*{Setting the drawing line size}

\noindent
\begin{tabularx}{\linewidth}{clcX}
\ikey{$>$}{increment}{Increment by one the size of the line.}
\ikey{$<$}{decrement}{Decrement by one the size of the line.}
\end{tabularx}

\vspace{\stretch{1}}

\newpage

\subsubsection*{Setting the kind of figure to draw}

In the setting mode pressing on of the following keys enter the (still
experimental) figure drawing mode:

\noindent
\begin{tabularx}{\linewidth}{clcX}
\ikey{v}{vertical line}{Draw a vertical line.}
\ikey{h}{horizontal line}{Draw a horizontal line.}
\ikey{s}{segment}{Draw a segment.}
\ikey{C}{circle}{Draw a circle.}
\ikey{p}{point}{Draw a point.}
\ikey{P}{polygone}{Draw a polygone.}
\ikey{f}{finish}{Close a polygone that is beeing drawn.}
\ikey{' '}{cancel}{Cancel the figure setting.}
\end{tabularx}

\vspace{\stretch{1}}



